\documentclass[10pt]{article}
\pagestyle{empty}

% --- tight margins (no geometry dependency)
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{10.3in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\textwidth}{7.0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\renewcommand\labelitemi{-}

\begin{document}

{\LARGE \textbf{Aaron Beavers}}\\
Independent Open-Source ML Systems Engineer (Evaluation / Experimentation / LLM Infrastructure)\\

\vspace{2pt}
\textbf{CONTACT}\\
West Des Moines, IA 50265 \;\;\textbar\;\; 515-388-0539 \;\;\textbar\;\; foamy125@gmail.com\\
GitHub: github.com/riatzukiza

\vspace{4pt}
\textbf{SUMMARY}\\
Independent engineer building reproducible ML evaluation pipelines, model-facing infrastructure, and compact experiment systems. Strongest patterns: deterministic runs, benchmark discipline, fast iteration on unusual technical problems, and shipping tooling that turns ideas into measurable results.

\vspace{2pt}
\textbf{SKILLS}\\
\textbf{ML/LLM}: benchmark harness design, dataset generation, embeddings (sentence-transformers), clustering (HDBSCAN), semantic search (Chroma), prompt-boundary evaluation, reasoning traces.\\
\textbf{Languages}: Clojure, Python, TypeScript/Node.js, SQL, Ruby.\\
\textbf{Systems}: Fastify/Express, Clojure CLI, Postgres, Docker, WebSockets, structured logging, local GPU/container workflows.\\
\textbf{Experimentation}: deterministic seeds, manifests, SHA-256 artifacts, run ledgers, search-space design, reproducible ablations.

\vspace{4pt}
\textbf{OPEN SOURCE / INDEPENDENT WORK}\\

\textbf{Parameter Golf Experiment Lab} --- Current independent work\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built an ACO-guided experiment lab that ranks Parameter Golf candidate recipes by hypothesis family, local proxy results, and leaderboard-derived motif signals.
  \item Implemented a local GPU runner and containerized runtime path to validate candidate configurations before spending cloud credits.
\end{itemize}

\textbf{Shibboleth} --- Generative adversarial prompt-eval dataset DSL \hfill \textit{github.com/octave-commons/shibboleth}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built a generative Clojure DSL + 7-stage pipeline to produce benchmark-grade adversarial prompt evaluation datasets with full provenance.
  \item Implemented leakage-proof train/dev/test splits via sentence-transformers embeddings + HDBSCAN clustering and cluster-disjoint stratified sampling.
  \item Emitted reproducibility bundles (Parquet, datasheet, manifests, SHA-256) so runs are auditable and repeatable.
\end{itemize}

\textbf{Open Hax Proxy} --- Multi-provider OpenAI-compatible LLM gateway \hfill \textit{github.com/open-hax/proxx}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Implemented an OpenAI-compatible proxy that routes by model prefix to OpenAI Responses, Anthropic Messages, and Ollama chat APIs.
  \item Preserved reasoning traces across API translations and added key/OAuth rotation plus semantic session search for easier experiment inspection.
\end{itemize}

\vspace{4pt}
\textbf{WORK EXPERIENCE}\\

\textbf{Raft Technologies} --- Full Stack Engineer (Python/Django + React) \hfill \textit{Jul 2020 -- Sep 2023}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built and maintained 5-stage Celery pipelines for uploaded-file processing (parse $\rightarrow$ validate $\rightarrow$ summarize $\rightarrow$ report $\rightarrow$ notify) with safe failure modes and operational visibility.
  \item Implemented robust file type + encoding detection and integrated anti-malware scanning automation (ClamAV REST) using retry/backoff + timeouts with persisted outcomes.
\end{itemize}

\textbf{CloudApp} --- Full Stack Engineer (Ruby on Rails) \hfill \textit{Sep 2018 -- Feb 2019}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Integrated a proprietary OCR service into a screenshot platform; shipped interactive OCR UX and hardened key flows with automated tests.
\end{itemize}

\textbf{Additional experience}: 1brand (Full Stack Engineer, 2019--2020); Birdseed (Full Stack Engineer, 2019); Freelance Software Engineer (2014--Present).

\vspace{4pt}
\textbf{EDUCATION / WORK AUTHORIZATION}\\
Valley Springs High School --- Diploma (2012) \;\textbar\; Authorized to work in the U.S. for any employer \;\textbar\; Willing to relocate.

\end{document}
