\documentclass[10pt]{article}
\pagestyle{empty}

% --- tight margins (no geometry dependency)
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{10.3in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\textwidth}{7.0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\renewcommand\labelitemi{-}

% (No external LaTeX packages: keep this file buildable on minimal TeX installs)

\begin{document}

{\LARGE \textbf{Aaron Beavers}}\\
Machine Learning / LLM Systems Engineer (Evaluation / LLM Infrastructure / Agentic Tooling)\\

\vspace{2pt}
\textbf{CONTACT}\\
West Des Moines, IA 50265 \;\;\textbar\;\; 515-388-0539 \;\;\textbar\;\; foamy125@gmail.com\\
GitHub: github.com/riatzukiza

\vspace{4pt}
\textbf{SUMMARY}\\
Applied ML + systems engineer with 10+ years of software experience (pre-LLM era). Build evaluation datasets, LLM gateway infrastructure, and simulation systems with a reliability-first mindset. Use agentic AI workflows to iterate faster while keeping changes testable and reproducible.

\vspace{2pt}
\textbf{SKILLS}\\
\textbf{ML/LLM}: prompt safety evaluation, dataset generation, embeddings (sentence-transformers), clustering (HDBSCAN), semantic search (Chroma), MT pipelines, reasoning traces.\\
\textbf{Languages}: Clojure, Python, TypeScript/Node.js, SQL, Ruby.\\
\textbf{Systems}: Fastify/Express, Postgres, Docker, WebSockets, React/Vite; OAuth PKCE, key rotation, retries/timeouts, manifests (SHA-256).

\vspace{4pt}
\textbf{OPEN SOURCE EXPERIENCE}\\

\textbf{Shibboleth} --- Generative adversarial prompt-eval dataset DSL (Clojure/Python) \hfill \textit{github.com/octave-commons/shibboleth}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built a generative DSL + 7-stage pipeline for publication-grade prompt-eval datasets with leakage-proof splits (sentence-transformers + HDBSCAN) and reproducible bundles (Parquet, datasheet, manifests, SHA-256).
\end{itemize}

\textbf{Open Hax Proxy} --- OpenAI-compatible LLM gateway \hfill \textit{github.com/open-hax/proxx}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Implemented OpenAI-compatible routing to OpenAI Responses, Anthropic Messages, and Ollama; preserved reasoning traces; added OAuth PKCE, rate-limit-aware account rotation, and Chroma-backed session recall.
  \item Reused the proxy + report stack in Mythloom, a worker-side anti-extractive resume analysis workbench for variant-vs-JD comparison.
\end{itemize}

\textbf{Ussyverse / Battlebussy (contributor)} --- AI CTF platform \hfill \textit{github.com/shuv1337/battlebussy}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Contributed production deployment + container hardening for Go + NATS JetStream control plane: multi-arch builds, GHCR publish, docker-compose prod, OCI Terraform/docs.
\end{itemize}

\textbf{Gates of Aker / Fantasia} --- Clojure simulation engine + React observability UI \hfill \textit{github.com/octave-commons/gates-of-aker}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Maintained a tick-based simulation backend with WebSocket control plane and React UI; wrote E2E tests; implemented agent perception/memory primitives (facet queries, cosine similarity) and belief propagation levers.
\end{itemize}

\vspace{4pt}
\textbf{WORK EXPERIENCE}\\

\textbf{Raft Technologies} --- Full Stack Engineer (Python/Django + React) \hfill \textit{Jul 2020 -- Sep 2023}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built and maintained 5-stage Celery pipelines for uploaded-file processing (parse $\rightarrow$ validate $\rightarrow$ summarize $\rightarrow$ report $\rightarrow$ notify) with safe failure modes and operational visibility.
  \item Implemented robust file type + encoding detection and integrated anti-malware scanning automation (ClamAV REST) using retry/backoff + timeouts with persisted outcomes.
\end{itemize}

\textbf{CloudApp} --- Full Stack Engineer (Ruby on Rails) \hfill \textit{Sep 2018 -- Feb 2019}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Integrated a proprietary OCR service into a screenshot platform; implemented interactive OCR UX (bounding boxes, click-to-extract text).
\end{itemize}

\textbf{Additional experience}: 1brand (Full Stack Engineer, 2019--2020); Birdseed (Full Stack Engineer, 2019); Freelance Software Engineer (2014--Present).

\vspace{4pt}
\textbf{EDUCATION}\\
Valley Springs High School --- Diploma (2012)

\vspace{2pt}
\textbf{WORK AUTHORIZATION}\\
Authorized to work in the U.S. for any employer. Willing to relocate.

\end{document}
