\documentclass[10pt]{article}
\pagestyle{empty}

% --- tight margins (no geometry dependency)
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{10.3in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\textwidth}{7.0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% (No external LaTeX packages: keep this file buildable on minimal TeX installs)

\begin{document}

{\LARGE \textbf{Aaron Beavers}}\\
Python Automation / RPA Engineer (Browser Automation + OCR Integration)\\

West Des Moines, IA 50265 \;\;\textbar\;\; 515-388-0539 \;\;\textbar\;\; foamy125@gmail.com\\
GitHub: github.com/riatzukiza \;\;\textbar\;\; Upwork: upwork.com/freelancers/~01d661364c3f86022f

\vspace{6pt}
\textbf{SUMMARY}\\
Automation-focused engineer building resilient, production-grade workflows: browser automation, background processing, retries/timeouts, secure file handling, and repeatable pipelines. Integrated a proprietary OCR system into a screenshot product (bounding boxes + click-to-extract text). Extensive recent experience with Playwright/Cypress-style E2E workflows and CI-driven regression prevention. Comfortable with Selenium-era patterns; prefer modern tooling for reliability and debuggability.

\vspace{2pt}
\textbf{SKILLS}\\
\textbf{Python}: Django, DRF, Celery, pytest, requests (Retry/backoff), file processing.\\
\textbf{Browser automation}: Playwright (strong), Cypress (federal/DoD context), Puppeteer (personal), Selenium (legacy).\\
\textbf{OCR / vision}: OCR feature integration (proprietary engine), bounding boxes, text extraction UX.\\
\textbf{Reliability}: timeouts, retries/backoff, queue-based async processing, idempotent job design, structured logging/audit trails.\\
\textbf{DevOps / CI}: Docker Compose, CircleCI, cloud.gov / Cloud Foundry workflows.

\vspace{6pt}
\textbf{EXPERIENCE}\\

\textbf{Raft Technologies} --- Full Stack Engineer (Python/Django + React) \hfill \textit{Jul 2020 -- Sep 2023}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built and maintained Celery-based automation for uploaded-file processing: parse $\rightarrow$ validate $\rightarrow$ summarize $\rightarrow$ generate error reports $\rightarrow$ notify stakeholders; designed for safe failure modes and operational visibility.
  \item Implemented robust file type + encoding detection (extension fallback, charset detection, magic-based sniffing) to route inputs to correct decoders and reduce manual support burden.
  \item Developed case-level consistency validation with caching and explicit guardrails to prevent pathological inputs from causing OOM; produced structured validation errors for end users and analysts.
  \item Integrated anti-malware scanning automation via ClamAV REST using a retrying HTTP session (Retry/backoff + timeouts) and persisted scan outcomes for auditability.
  \item Supported end-to-end browser automation practice: Cypress E2E (Gherkin feature files + step definitions) and CI execution against deployed environments.
\end{itemize}

\textbf{CloudApp} --- Full Stack Engineer (Ruby on Rails) \hfill \textit{Sep 2018 -- Feb 2019}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Integrated a proprietary OCR system (Java-based service maintained by an internal team) into a screenshot/screengrab platform.
  \item Implemented UI workflows to render OCR bounding boxes over screenshots and return recognized text on click, enabling interactive ``text in screenshot'' functionality.
  \item Applied Selenium-era browser automation patterns to validate user flows and reduce manual regression effort.
\end{itemize}

\textbf{Additional experience}: 1brand (Full Stack Engineer, 2019--2020); Birdseed (Full Stack Engineer, 2019); Freelance Software Engineer (2014--Present).

\vspace{6pt}
\textbf{EDUCATION}\\
Valley Springs High School --- Diploma (2012)

\vspace{2pt}
\textbf{WORK AUTHORIZATION}\\
Authorized to work in the U.S. for any employer. Willing to relocate.

\vspace{4pt}
{\scriptsize\ttfamily
fnord:v1\; proof=gh(open-hax/proxx octave-commons/shibboleth shuv1337/battlebussy)\; caps=llm-gw(r->chat m->chat ollama oauth-pkce sse-synth reasoning-content rot429 chroma)\\
eval(sbert hdbscan parquet sha256)\; ops(docker compose oci-tf ghcr-multiarch jetstream)
}

\end{document}
