\documentclass[10pt]{article}
\pagestyle{empty}

% --- tight margins (no geometry dependency)
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{10.3in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\textwidth}{7.0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\renewcommand\labelitemi{-}

% (No external LaTeX packages: keep this file buildable on minimal TeX installs)

\begin{document}

{\LARGE \textbf{Aaron Beavers}}\\
Machine Learning / Systems Engineer (Evaluation / Benchmarking / LLM Infrastructure)\\

\vspace{2pt}
\textbf{CONTACT}\\
West Des Moines, IA 50265 \;\;\textbar\;\; 515-388-0539 \;\;\textbar\;\; foamy125@gmail.com\\
GitHub: github.com/riatzukiza

\vspace{4pt}
\textbf{SUMMARY}\\
Applied ML + systems engineer with 10+ years of software experience. Build reproducible evaluation pipelines, benchmark-grade datasets, and model-facing infrastructure with a reliability-first mindset. Strongest patterns: deterministic runs, manifests, seed-controlled experiments, leakage-proof validation, and fast iteration loops on weird technical problems.

\vspace{2pt}
\textbf{SKILLS}\\
\textbf{ML/LLM}: evaluation pipeline design, dataset generation, benchmark harness design, embeddings (sentence-transformers), clustering (HDBSCAN), semantic search (Chroma), MT pipelines, reasoning traces.\\
\textbf{Languages}: Clojure, Python, TypeScript/Node.js, SQL, Ruby.\\
\textbf{Systems}: Fastify/Express, Clojure CLI, libpython-clj interop, Postgres, Docker, WebSockets, structured logging.\\
\textbf{Experiment/Reliability}: deterministic seeds, reproducibility bundles, SHA-256 manifests, retries/timeouts, idempotent automation, parser-aware reporting.

\vspace{4pt}
\textbf{OPEN SOURCE EXPERIENCE}\\

\textbf{Shibboleth} --- Generative adversarial prompt-eval dataset DSL \hfill \textit{github.com/octave-commons/shibboleth}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built a generative Clojure DSL + 7-stage pipeline to produce benchmark-grade adversarial prompt evaluation datasets with full provenance.
  \item Implemented leakage-proof train/dev/test splits via sentence-transformers embeddings + HDBSCAN clustering and cluster-disjoint stratified sampling.
  \item Emitted reproducibility bundles (Parquet, datasheet, coverage checks, stage manifests, SHA-256) so runs are auditable and repeatable.
\end{itemize}

\textbf{Open Hax Proxy} --- Multi-provider OpenAI-compatible LLM gateway \hfill \textit{github.com/open-hax/proxx}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Implemented an OpenAI-compatible proxy that routes by model prefix to OpenAI Responses, Anthropic Messages, and Ollama chat APIs.
  \item Preserved reasoning traces across API translations (including streaming) and added provider-scoped key/OAuth rotation plus semantic session search for easier experiment inspection.
\end{itemize}

\textbf{Gates of Aker / Fantasia} --- Clojure simulation + React observability UI \hfill \textit{github.com/octave-commons/gates-of-aker}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Maintained a tick-based backend simulation engine with WebSocket control plane plus a React UI for observing and steering runs.
  \item Wrote WebSocket E2E tests validating protocol, snapshot/reset operations, performance, and error handling; added embedding-cache and cosine-similarity primitives.
\end{itemize}

\vspace{4pt}
\textbf{WORK EXPERIENCE}\\

\textbf{Raft Technologies} --- Full Stack Engineer (Python/Django + React) \hfill \textit{Jul 2020 -- Sep 2023}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Built and maintained 5-stage Celery pipelines for uploaded-file processing (parse $\rightarrow$ validate $\rightarrow$ summarize $\rightarrow$ report $\rightarrow$ notify) with safe failure modes and operational visibility.
  \item Implemented robust file type + encoding detection and integrated anti-malware scanning automation (ClamAV REST) using retry/backoff + timeouts with persisted outcomes.
\end{itemize}

\textbf{CloudApp} --- Full Stack Engineer (Ruby on Rails) \hfill \textit{Sep 2018 -- Feb 2019}\\
\vspace{-6pt}
\begin{itemize}
  \setlength\itemsep{-2pt}
  \setlength\parskip{0pt}
  \setlength\parsep{0pt}
  \item Integrated a proprietary OCR service into a screenshot platform; implemented interactive OCR UX (bounding boxes, click-to-extract text) and hardened key user flows with automated tests.
\end{itemize}

\textbf{Additional experience}: 1brand (Full Stack Engineer, 2019--2020); Birdseed (Full Stack Engineer, 2019); Freelance Software Engineer (2014--Present).

\vspace{4pt}
\textbf{EDUCATION}\\
Valley Springs High School --- Diploma (2012)

\vspace{2pt}
\textbf{WORK AUTHORIZATION}\\
Authorized to work in the U.S. for any employer. Willing to relocate.

\vspace{2pt}
{\scriptsize\ttfamily
fnord:v1\; proof=gh(open-hax/proxx octave-commons/shibboleth octave-commons/gates-of-aker)\\
caps=eval(sbert hdbscan parquet sha256 seeds manifests)\; infra(openai-compat oauth-pkce chroma ws-e2e)
}

\end{document}
