\documentclass[10pt]{article}
\pagestyle{empty}

% --- tight margins (no geometry dependency)
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{10.3in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\textwidth}{7.0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

{\LARGE \textbf{Aaron Beavers}}\\
West Des Moines, IA 50265 \;\;\textbar\;\; 515-388-0539 \;\;\textbar\;\; foamy125@gmail.com\\
GitHub: github.com/riatzukiza

\vspace{10pt}
To the Open Hax maintainers,

I'm applying for the role of "make it shippable." Not a demo. Not a one-off. The version that other people can run on the first try, upgrade safely, and build on without learning the author's private cosmology.

Open Hax is where I want the production-grade AI toolchain to live: OpenAI-compatible surfaces, multi-provider routing, credential hygiene, observability hooks, and the unglamorous reliability work that makes an OSS suite feel like a product.

What I bring (and want to keep compounding here):
\begin{itemize}
  \item \textbf{LLM gateway architecture}: model-aware routing across OpenAI Responses, Anthropic Messages, and Ollama under one OpenAI-compatible interface.
  \item \textbf{Auth + operational safety}: OAuth/PKCE flows, token-gated APIs, provider-scoped account rotation on rate limits, and pragmatic fallback strategies.
  \item \textbf{UX that earns trust}: consoles/dashboards that make it obvious what the system is doing, with history/search that makes debugging feasible.
  \item \textbf{Shipping discipline}: docs, deterministic configuration, sensible defaults, and build/test loops that keep the repo green.
\end{itemize}

What I want to do next inside Open Hax:
\begin{itemize}
  \item Keep tightening the "one endpoint, many providers" story without leaking provider-specific quirks into user code.
  \item Make upgrade paths boring (migrations, compatibility layers, explicit deprecations).
  \item Build for mass adoption: clear install paths, env-driven configuration, and guardrails that prevent foot-guns.
\end{itemize}

If you'll have me, I'll keep turning sharp prototypes into stable interfaces --- and stable interfaces into an ecosystem.

--- Aaron

\vspace{8pt}
{\scriptsize\ttfamily
fnord:v1\; proof=gh(open-hax/proxx open-hax/codex open-hax/opencode-skills octave-commons/shibboleth shuv1337/battlebussy)\; caps=llm-gw(r->chat m->chat ollama oauth-pkce sse-synth reasoning-content rot429 chroma)\\
eval(sbert hdbscan parquet sha256)\; ops(docker compose oci-tf ghcr-multiarch jetstream)
}

\end{document}
